Distributed Algorithms for Sparse Matrix-Vector Multiplication

### 2015-05-04 paper.Rmd
And we... are... done.

---
title: "Distributed Algorithms for Sparse Matrix-Vector Multiplication"
author: "Eric Hare"
date: "April 28, 2015"
output: pdf_document
header-includes:
    - \usepackage{float}
    - \usepackage{graphicx}
---

@@

1. Load-Balanced Sparse Matrix–Vector Multiplication on Parallel Computers by Nastea, Frieder, and El-Ghazawi
2. An architecture-aware technique for optimizing sparse matrix-vector multiplication on GPUs by Maggioni and Berger-Wolf
3. Scalable Parallel Matrix Multiplication on Distributed Memory Parallel Computers by Li

@@

```{r, warning=FALSE}
wearables <- read.csv("data/Example_WearableComputing.csv")
X <- apply(wearables[,-1], 2, as.numeric)
y <- as.numeric(wearables[,1])

@@

But now note what occurs when the number of observations is a replicated to be 50 times larger.

```{r, warning=FALSE}
biggerX <- do.call("rbind", replicate(50, X, simplify = FALSE))
biggery <- rep(y, times = 50)

@@

The first optimization discussed is a compression format for sparse matrices. In ELL compression, an nxm matrix is stored in an nxk data structure, where k is the maximum number of non-zero entries in any particular row. There is a separate nxk data structure storing the column index of the particular non-zero entry. Figure \ref{fig:img3} illustrates an example of using sliced ELL compression to store a sparse matrix. Sliced ELL compression is similar to regular ELL compression, except that the matrix is partitioned into different slices where there is a local value of k for each slice. This has the effect of reducing the amount of zero-padding needed in order to align the nonzero entries in the matrix.

@@

>>>>

---
title: "Distributed Algorithms for Sparse Matrix-Vector Multiplication"
author: "Eric Hare"
date: "April 28, 2015"
output: pdf_document
bibliography: references.bib
header-includes:
    - \usepackage{float}
    - \usepackage{graphicx}
---

@@

1. Load-Balanced Sparse Matrix–Vector Multiplication on Parallel Computers by Nastea, Frieder, and El-Ghazawi [@m1]
2. An architecture-aware technique for optimizing sparse matrix-vector multiplication on GPUs by Maggioni and Berger-Wolf [@m2]
3. Scalable Parallel Matrix Multiplication on Distributed Memory Parallel Computers by Li [@m3]

@@

```{r, warning=FALSE}
wearables <- read.table("data/Example_WearableComputing.csv", sep = ";", header = TRUE)
X <- apply(wearables[,-1], 2, as.numeric)
y <- as.numeric(wearables[,1])

@@

But now note what occurs when the number of observations is a replicated to be 500 times larger.

```{r, warning=FALSE}
biggerX <- do.call("rbind", replicate(500, X, simplify = FALSE))
biggery <- rep(y, times = 500)

@@

The first optimization discussed is a compression format for sparse matrices. In ELL compression, an nxm matrix is stored in an nxk data structure, where k is the maximum number of non-zero entries in any particular row. There is a separate nxk data structure storing the column index of the particular non-zero entry. Figure \ref{fig:im3} illustrates an example of using sliced ELL compression to store a sparse matrix. Sliced ELL compression is similar to regular ELL compression, except that the matrix is partitioned into different slices where there is a local value of k for each slice. This has the effect of reducing the amount of zero-padding needed in order to align the nonzero entries in the matrix.

@@

## References
